Connecting Documents to Ideas

### 2008-08-27 papers/web_of_ideas/web_of_ideas.tex

\subsubsection{User Interface Redesign}
The first user study demonstrated a few flaws in the application's user interface. These problems can be generalized as:
\begin{itemize}
	\item \textbf{People need to easily visualize the the hierarchy of points, topics, and relationships.} A significant portion of the participants ($5/12$) explicitly expressed confusion about not being able to view the entire hierarchy of topics and points, and felt lost when looking at the individual point or topic pages. In this view, each point and topic is visually separated from its related points and topics, and thus users did not understand the significance of these individual pages. Viewing related points as lists of {\it child} and {\it parent} points was confusing to three of the eight people who used the second version of the UI. This ``flattened'' perspective also makes it difficult to relate several points to another. Most of the users who linked points together ($5/7$) did not recognize the need to first create an intermediate point and then relate other points to that new point. An easier model for grouping and associating objects together is necessary.
	\item \textbf{People need better organization capabilities at snippet creation time.}
\end{itemize}

% motivation for file save-as in snippet dialog
\idea{people want to do most of their organization during the snippet creation process}
\idea{people want to be able to create subtopics right away}
\idea{specific topics used by different users are more likely not to be recreated}

>>>>

\subsubsection{User Interface Redesign}
The first user study demonstrated a few flaws in the application's user interface. These problems can be generalized as:
\begin{itemize}
	\item \textbf{People need to easily visualize the the hierarchy of points, topics, and relationships.} A significant portion of the participants ($5/12$) explicitly expressed confusion about not being able to view the entire hierarchy of topics and points, and felt lost when looking at the individual point or topic pages. In this view, each point and topic is visually separated from its related points and topics, and thus users did not understand the significance of these individual pages. Viewing related points as lists of {\it child} and {\it parent} points was confusing to three of the eight people who used the second version of the UI. This ``flattened'' perspective also makes it difficult to relate several points to another. Most of the users who linked points together ($5/7$) did not recognize the need to first create an intermediate point and then relate other points to that new point. An easier model for grouping and associating objects together is necessary.
	\item \textbf{People need better organization capabilities at snippet creation time.} Only a few ($3/12$) users went back to their {\it Recent Activity} to create additional topics when organizing, which suggests that a majority of users prefer to place snippets within topics when they are first created. However, if users are only allowed to assign a snippet to one topic without context of a topic hierarchy, they may create a very specific topic that is unlikely to be used by another person. We observed this behavior with two participants who both created snippets regarding a politician's controversial affair, but whose snippets did not belong to related topics. Several participants ($4/12$) remarked that they were unsure how broad a topic should be. By allowing users to create and traverse the topic hierarchy, they would be able to more easily organize and specify new topics when creating a snippet.
\end{itemize}
